ESBMC-GPU \\ A Context-Bounded Model Checking Tool \\ to Verify CUDA Programs

### 2017-05-15 Publications/Original Software Publications/Science of Computer Programming/source/manuscript.tex
updating conclusion
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

ESBMC-GPU marks the first application of an SMT-based context-BMC tool that recognizes CUDA directives~\cite{pereira:2016}. \textcolor{blue}{Besides, it also applies MPOR, two-thread analysis, and state hashing in order to further simplify verification models and provides fewer incorrect results, compared with GKLEE, GPUVerify, and CIVL.} Finally, it presents improved ability to detect array out-of-bounds and data race violations. Future work aims to support stream interleaving and implement further techniques to reduce the number of thread interleavings, by taking into account GPU symmetry.

>>>>

ESBMC-GPU marks the first application of an SMT-based context-BMC tool that recognizes CUDA directives~\cite{pereira:2016}. \textcolor{blue}{Besides, it also applies MPOR, two-thread analysis, and state hashing in order to further simplify verification models and provides fewer incorrect results, compared with GKLEE, GPUVerify, and CIVL.} Finally, it presents improved ability to detect array out-of-bounds and data race violations. Future work aims to support \textcolor{blue}{CUDA (parallel) streams and events~\cite{cuda:2012}} and implement further techniques to reduce the number of thread interleavings, by taking into account GPU symmetry.
